A new method to explicitly estimate the shift of optimum in multispecies studies

### 2022-01-25 redaction/manuscript.Rmd
Change keywords and order them + thirty -> 30 in accord with guidelines

2) We extended an existing model to explicitly estimate optimum shifts for multiple species. We called this new Bayesian hierarchical model the Explicit Hierarchical Model of Optimum Shifts (EHMOS). In a simulation study, we compared its accuracy to a mean comparison method and a Bayesian generalized linear mixed model (GLMM). Specifically, we tested if the accuracy of the methods was sensitive to (1) sampling design, (2) species optimum position, and (3) species ecological specialization. In addition, we compared the three methods using a real dataset of investigated optimum shifts in 24 Orthopteran species between two surveys conducted thirty years apart along an elevation gradient in the French Alps.

@@

**Keywords:** species optimum shift, Bayesian hierarchical modelling, species-environment relationship, gradient analysis, species response curve, sampling design, GLMM, mean comparison method

>>>>

2) We extended an existing model to explicitly estimate optimum shifts for multiple species. We called this new Bayesian hierarchical model the Explicit Hierarchical Model of Optimum Shifts (EHMOS). In a simulation study, we compared its accuracy to a mean comparison method and a Bayesian generalized linear mixed model (GLMM). Specifically, we tested if the accuracy of the methods was sensitive to (1) sampling design, (2) species optimum position, and (3) species ecological specialization. In addition, we compared the three methods using a real dataset of investigated optimum shifts in 24 Orthopteran species between two surveys conducted 30 years apart along an elevation gradient in the French Alps.

@@

**Keywords:** Bayesian hierarchical modelling, Generalized Linear Mixed Model (GLMM), gradient analysis, mean comparison method, sampling design, species ecological specialization, species optimum shift, species response curve
